{{ cookiecutter.paper_title}}

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Updated files for the Cookiecutter in general
Fixing jinja2 error with extra curly braces
Trying to remove annoying curly brackets

%% Paper title
\title{ {{ cookiecutter.paper_title}}}

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{{{cookiecutter.author_email}}}}\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}

>>>>

%% Paper title
\title{ {{ cookiecutter.paper_title}} }

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}
